Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-10-18 paper/ms.tex
Added a sentence on the history of the progenitors at the suggestion of Dean.

The simulations performed for this study consisted of a suite of
30 two-dimensional simulations of thermonuclear supernova explosions 
from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
were compared to a suite of supernova simulations from traditional C-O 
progenitors. {\color{blue} The C-O progenitors are parameterized and 
include the effects of convective ``simmering" in the core as the WD 
approaches the Chandrasekhar mass~\citep{Chametal08,PiroBild08,jacketal2010}.
Using parameterized C-O models allowed us to choose conditions, e.g.\
central density, to control differences between the hybrid and traditional 
models and thus assess the effect of the hybrid structure.
}

>>>>

The simulations performed for this study consisted of a suite of
30 two-dimensional simulations of thermonuclear supernova explosions 
from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
were compared to a suite of supernova simulations from traditional C-O 
progenitors. {\color{blue} The C-O progenitors are parameterized and 
include the effects of convective ``simmering" in the core as the WD 
approaches the Chandrasekhar mass~\citep{Chametal08,PiroBild08,jacketal2010}.
Using parameterized C-O models allowed us to choose conditions, e.g.\
central density, to control differences between the hybrid and traditional 
models and thus assess the effect of the hybrid structure.}
{\color{green}
The central density at ignition depends on both the carbon abundance 
and the binary history, mainly cooling time before accretion 
\citep{Kruegeretal2012}, and so this comparison does not correspond 
to a comparable binary scenario, but is intended as a more 
straightforward comparison.
}
